---
title: "Quarto template"
---

This is a Quarto template for multi-language website. We present below example with R and Python.

# Setup

::: {.panel-tabset group="language"}
## R

```{r}
#| code-summary: "Load R packages"
#| code-fold: show
#| message: false
#| warning: false

library(dplyr)
library(ggplot2)
```

## Python

```{python}
#| code-summary: "Load Python packages"
#| code-fold: show
#| message: false
#| warning: false

import pandas as pd
import seaborn as sns
import matplotlib.pyplot as plt
import session_info
```

:::

# The pinguin dataset

The goal of palmerpenguins is to provide a great dataset for data exploration & visualization.

::: {.panel-tabset group="language"}
## R

::: panel-tabset
### Description

```{r}
#| R.options:
#|  knitr.kable.NA: ""

dt <- read.csv("./docs/data/palmer-penguins.csv") %>%
  mutate(
    species = factor(species),
    island = factor(island),
    sex = factor(sex)
  )

dt %>%
  summary() %>%
  knitr::kable()
```

### Structure

```{r}
str(dt)
```

### Overview

```{r}
dt
```

:::

## Python

::: panel-tabset
### Description

```{python}
df = pd.read_csv('./docs/data/palmer-penguins.csv')

df.describe(include='all')
```

### Structure

```{python}
df.info()
```

### Overview

```{python}
df
```

:::
:::

# Visualization

::: {.panel-tabset group="language"}
## R

See @fig-r for an exploration of bill sizes by species.

```{r}
#| warning: false
#| label: fig-r
#| fig-cap: "Bill length and depth for Adelie, Chinstrap and Gentoo Penguins at Palmer Station LTER"
#| fig-width: 8
#| fig-height: 6

ggplot(dt, aes(x = bill_length_mm, y = bill_depth_mm, color = species, fill = species)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = "lm", formula = y ~ x, se = T, show.legend = F) +
  scale_discrete_manual(aesthetics = c("colour", "fill"), values = c("darkorange","purple","cyan4")) +
  labs(x = "Bill length (mm)",
       y = "Bill depth (mm)",
       color = "Penguin species",
       fill = "Penguin species") +
  theme_bw()
```

## Python

See @fig-python for an exploration of bill sizes by species.

```{python}
#| label: fig-python
#| fig-cap: "Bill length and depth for Adelie, Chinstrap and Gentoo Penguins at Palmer Station LTER"
#| fig-width: 8
#| fig-height: 6

sns.set_style('whitegrid')

(
  sns.lmplot(x = "bill_length_mm",
               y = "bill_depth_mm",
               hue = "species",
               height = 7,
               data = df,
               palette = ['#FF8C00','#159090','#A034F0'])
  .set_xlabels('Bill length (mm)')
  .set_ylabels('Bill depth (mm)')
);

plt.show()
```

:::

::: {.callout-note collapse="true" title="Session information"}
::: {.panel-tabset group="language"}
# R

```{r}
sessionInfo()
```


# Python

```{python}
session_info.show() # html=False
```

:::
:::